Caveat Emptor: light curves of the brightest stars in the \\ Southern sky as seen by bRing

### 2023-09-27 src/tex/ms.tex
[showyourwork] overleaf sync

   \title{Caveat Emptor: Light curves of the brightest stars in the \\ Southern sky as seen by bRing}

@@

>>>>

   \title{Caveat Emptor: light curves of the brightest stars in the \\ Southern sky as seen by bRing}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/84810.pdf}
    \caption{Example of a variable star seen in all the cameras.
    %
    Top panel is all combined light curves, lower panels are the individual cameras.}
    \label{fig:cleaned_output}
    \script{plot_lightcurves.py}
\end{figure*}
